Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-05-07 MS.tex
Add asterix to example references
MS change

@@

@@

\todo[inline,color=white]{1. need to delete references 50/50: DONE}

\todo[inline,color=white]{2. need to reduce nb words abstract 148/150: DONE}

\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation: DONE}

\todo[inline, color=white] {4.  re write Appendix A growth equation : DONE}

\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub: DONE}

\todo[inline, color=white] {6. to add the list of traits/stage categories combination for which we identified a need of more data in the last paragraph of the discussion: DONE}

\todo[inline, color=white] {7. to add subsections in Discussion: DONE}

@@

\todo[inline, color=white] {10. To delete discussion about references in coverletter: DONE}

@@

\todo[inline, color=white] {12. to check the number of word in figures legends (less than 150): DONE}

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species and under non-stressed conditions. A "complete" dataset (n=328 vs n=198) also included correlations measured at within-species level, and under stressed conditions, and spanning different plant stages. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. 2. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of low light on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even with 7 additional correlations measured under low light conditions.

@@

For the correlation between Aarea and growth, to our knowledge no study has previously assessed this in relation to plant size. In the growth model (Appendix \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate. We noted no signal of an effect of low light on the positive correlation between Aarea and growth rate in juvenile plants.

@@

\begin{appendices} \label{sec:appendices}

@@

We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass ($m_t$, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}). These size dimensions are routinely measured on seedling and adult plants. Here we provide a brief overview of the model; an upcoming publication will elaborate further on the predicted relationships between traits and growth rate.

@@

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7e.pdf}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7d.pdf}
\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1, as recorded by the authors), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). n= number of correlation r reported. Abbreviation: across veg= more than 2 vegetation types, boreal\&temp= boreal and temperate deciduous forest, med= Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp= temperate deciduous, temp rain= temperate rain, trop rain= tropical rain, trop seas= tropical seasonal forests, GR= growth rate and RGR= relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA). AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{FigA7}
\end{figure}

>>>>

This study is the first one of an upcoming series performed by the authors on the same thematic: the insertion of plant size in functional ecology. Daniel Falster will develop more deeply a growth model and tested hypotheses using expended dataset on growth and traits in one site. Emma Gray and Ian Wright are working on this thematic across all plant growth forms (tree, grass and shrub), and different environements.

@@

shows predictable changes with plant size of the correlations

@@

@@

@@

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species and under non-stressed conditions. A "complete" dataset (n=328 vs n=198) also included correlations measured at within-species level, and under stressed conditions, and spanning different plant stages. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. 2. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added.

@@

For the correlation between Aarea and growth, to our knowledge no study has previously assessed this in relation to plant size. In the growth model (Appendix \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate. In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.

@@

\begin{Appendix} \label{sec:textbox}

@@

We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass ($m_t$, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}). These size dimensions are routinely measured on seedling and adult plants.

@@

\newpage
\begin{Supplemnetary material}\label{sec:appendices}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7d.pdf}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7e.pdf}
\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1, as recorded by the authors), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). n= number of correlation r reported. Abbreviation: across veg= more than 2 vegetation types, boreal\&temp= boreal and temperate deciduous forest, med= Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp= temperate deciduous, temp rain= temperate rain, trop rain= tropical rain, trop seas= tropical seasonal forests, GR= growth rate and RGR= relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA). AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. Smallest is the AIC better is the model. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{FigA7}
\end{figure}
